---
title: "homr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressPackageStartupMessages({
  library(rnaturalearth)
  library(rnaturalearthdata)
  library(homr)
  library(sf)
  library(ggplot2)
  library(dplyr)
  })
```


An R package for querying and accessing [Historical Observing Metadata Repository](https://www.ncei.noaa.gov/access/homr/api).

Search within a state; it is much faster when `headerOnly = TRUE`.  Note that we include the option to attach (as an attribute) the definitions table. It's not clear how this might be useful, but it is available. By default `include_definitions = FALSE`.

```{r}
x = query_search(headersOnly = "true", state = "ME", include_definitions = TRUE) |>
 glimpse()
```

Above you'll note that `startDate` and `endDate` are both character type.  That's because the are entries like 'present' and 'unknown'.

Below we show the definitions table.

```{r}
attr(x, 'homr_definitions') |>
  glimpse()
```

We can map these...

```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")
ggplot(data = world) +
  geom_sf() +
  xlim(-72, -63) +
  ylim(42, 48) +
  geom_sf(data = x, aes(alpha = 0.5)) +
  theme(legend.position = "none") 
```