---
title: "homr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

An R package for querying and accessing [Historical Observing Metadata Repository](https://www.ncei.noaa.gov/access/homr/api).
  + [R v4.1+](https://www.r-project.org/)
  + [rlang](https://CRAN.R-project.org/package=rlang)
  + [httr](https://CRAN.R-project.org/package=httr)
  + [sf](https://CRAN.R-project.org/package=sf)
  + [dplyr](https://CRAN.R-project.org/package=dplyr)


### Simple usage

```{r}
suppressPackageStartupMessages({
  library(rnaturalearth)
  library(rnaturalearthdata)
  library(homr)
  library(sf)
  library(ggplot2)
  library(dplyr)
  })
```


Search for sites within a state. 

##### Tip - speed your searches
It is much faster when you specify `headerOnly = TRUE` (which is the default).

##### Tip - optionally retrieve a table of definitions
Note that for demonstration purposes we include the option to attach (as an attribute) the definitions table. It's not clear how this might be useful, but it is available. By default `definitions = FALSE` so it is not included. 


```{r}
x = query_search(state = "ME", definitions = TRUE) |>
 glimpse()
```

Above you'll note that `startDate` and `endDate` are both character type.  That's because the are entries like 'present' and 'unknown'.

Below we show the definitions table.

```{r}
attr(x, 'homr_definitions') |>
  glimpse()
```


### Searching multiple states

It seems the only geographical filter is by state/province. So to get multiple states/provinces you could try iterating.  Note the small pause for each iteration; if it goes too quickly the server can't seem to keep up.

```{r}
places = c("NS","NB","ME","NH","MA")
x = lapply(places, function(place) {Sys.sleep(2) ; query_search(state = place)} ) |>
  dplyr::bind_rows()
```

We can map these stations...

```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")
bb <- sf::st_bbox(x)
ggplot(data = world) +
  geom_sf() +
  xlim(bb$xmin, bb$xmax) +
  ylim(bb$ymin, bb$ymax) +
  geom_sf(data = x, aes(alpha = 0.5)) +
  theme(legend.position = "none") 
```

... well, miscoding of attributes happens!